---
title: "bcs"
author: "Giacomo"
date: "23 Oct 2015"
output: ioslides_presentation
runtime: shiny 
---

```{r, echo=FALSE}
library(ggplot2)
library(RColorBrewer)
library(shiny)
library(dplyr)
kol = brewer.pal(12, 'Set3')
seqD1 = read.csv('data/seqD1.csv')
seqDay5 = read.csv('data/seqDay5.csv')
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r, echo = FALSE}
shinyApp(
  
  ui = fluidPage(
    selectInput("region", "Region:", 
                choices = colnames(WorldPhones)),
    plotOutput("phonePlot")
  ),
  
  server = function(input, output) {
    output$phonePlot <- renderPlot({
      barplot(WorldPhones[,input$region]*1000, 
              ylab = "Number of Telephones", xlab = "Year")
    })
  },
  
  options = list(height = 500)
)

```

## Slide with R Code and Output

<iframe width="600" height="371" seamless frameborder="0" scrolling="no" src="https://docs.google.com/spreadsheets/d/1oVralALYTKKIXmAo3TCdz039nN_aNeeAPAJl_2EqXng/pubchart?oid=1691385512&amp;format=interactive"></iframe>

## Slide with R Code and Output

```{r, echo=FALSE}
shinyApp(
  ui = fluidPage(
    sliderInput("time",
                "Choose the time of the day",
                min = 1,
                max = 1440,
                value = c(1,1440)),
    plotOutput("sequence")
  ),
  
  server = function(input, output) {
    output$sequence <- renderPlot({
      x = seq(from = min(input$time), to = max(input$time), by = 1)
      p = ggplot( seqD1[seqD1$Time %in% c(x), ] , aes(x = Time, fill = factor(av), y = SharePerHour)) + geom_bar(stat = "identity", width = 1) + scale_fill_manual(values=kol) + theme_minimal()
      print(p)
    })
  }, 
  options = list(height = 1000)
)
```



## Slide with R Code and Output

```{r, echo=FALSE}
shinyApp(
  ui = fluidPage(
    sliderInput("timescale",
                "Choose the time of the day",
                min = 480,
                max = 1440,
                step = 10, 
                animate = animationOptions(interval=400, loop=TRUE), 
                value = 1),  
    plotOutput("sequence")), 
  
  server = function(input, output) {
    output$sequence <- renderPlot({
      ggplot( seqD1[seqD1$Time %in% c(input$timescale), ] , aes(x = av, fill = factor(av), y = SharePerHour)) + geom_bar(stat="identity") + scale_fill_manual(values=kol) + theme_minimal() + ylim(0,50) + scale_x_discrete(drop=FALSE) 
    })
  }, 
  options = list(height = 1000)
)
```

## ff

<iframe src="timefriday.html"></iframe>

## ff

```{r, echo=FALSE}

shinyApp(
  ui = fluidPage(
    sliderInput("time",
                "Choose the time of the day",
                min = 1,
                max = 1440,
                value = c(1,1440)),
    plotOutput("sequence")
  ),
  
  server = function(input, output) {
    output$sequence <- renderPlot({
      x = seq(from = min(input$time), to = max(input$time), by = 1)
      p = ggplot( seqD1[seqD1$Time %in% c(x), ] , aes(x = Time, fill = factor(av), y = SharePerHour)) + geom_bar(stat = "identity", width = 1) + scale_fill_manual(values=kol) + theme_minimal()
      print(p)
    })
  }, 
  options = list(height = 1000)
)

```



